Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-21 doc/manuscript/ESSDmanuscript.Rmd
add a bit of text
Update ESSDmanuscript.Rmd

@@

@@

To support export of data to EFDB, and to improve the overall quality of the ForC database, we added ten increment variables, implemented some modest restructuring, resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

## Increment variables
We added ten increment variables to the set of named and defined variables (or 20, counting _OM and _C versions), which previously included only one (aboveground biomass increment, *delta.agb*). 
*(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)*
These are directly related to C stocks as previously defined in ForC, with "*delta.*" added in front of the variable name.

@@

>>>>

Dead organic matter includes all non-living biomass that is not within the mineral soil layer and smaller than the litter size threshold.

Dead wood is defined as...

@@

Soil organic matter is defined as...

@@

To support export of data to EFDB, and to improve the overall quality of the ForC database, we defined ## new variables, implemented some modest restructuring, resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

## Defining new variables

We added eleven increment variables to the set of named and defined variables (or 22, counting _OM and _C versions), which previously included only one (aboveground biomass increment, *delta.agb*). 
*(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)*
These are directly related to C stocks as previously defined in ForC, with "*delta.*" added in front of the variable name.

@@

We clarified the definition of *organic.layer* (O-horizon, including *litter*) and added the variable *litter* (relatively undecomposed plant material/ OL horizon).
